Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-22 theory.tex
adding case C equation

As the cuts values change, the flow rate between the different stage has to be
recomputed. Because the cascade is not reorganised (the number of cascade per
stage remain the same as the original design). The new flow rate are computed as the flow rate of cascade

>>>>

As the cuts values change, the flow rate between the different stage has to be
recomputed. Because the cascade is not reorganised (the number of cascade per
stage remain the same as the original design). The new flow rate are computed as
the flow rates of the reconfigured cascade scaled down by the possible
flows of the original one: the flow rates of a reconfigured cascade are
computed, the ratios of the flow stage by stage with the original are determined,
the smaller ratio is used to scale down all the flow rates.

\subsubsection{Case C}
The last model assumes that the tail to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $gamma$ and the cut $theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:

\begin{equation}\label{eq:gamma_p}
\gamma(1-N')(P\theta-N) - N'(1-(N'\theta-N)/(-1+\theta))(-1+\theta) = 0
\end{equation}

The only solution allowing product assay values ranging between 0 and 1 is the
following :
\begin{equation}\label{eq:model_b_sol}
    \frac{\gamma(N + \theta) - N 
            - \sqrt{\gamma^2(N^2 
                            - 2N\theta 
                            + \theta^2) 
                    - \gamma(2N^2 - 2\theta^2 
                            + 2N + 2\theta) 
                    + N^2 + 2N\theta + \theta^2 - 2N - 2\theta + 1} 
            - \theta + 1}
        {2\theta(\gamma - 1)}
\end{equation}

The last model is very similar to the model A.
